### 2016-01-09 phd/sop/toronto.tex
research proposal for MRG

Artificial Intelligence has always tantalized me. Long before understanding what computer science stands for I wondered why AI has not been achieved yet. To explore it further, I enrolled in BSc in Robotics at the best technical university in my country. I studied maths, physics and mechanics, material science and manufacturing technologies; programming and software-oriented courses were my favourite, however. Paired with my passion for vision and perception, which I have developed as a photojournalist, it steered me towards my first computer vision course. I immediately knew that this intersection of image processing and machine learning was the area I wanted to focus on. It became apparent that pursuing a PhD was one of the few ways that could get me closer to solving the AI challange.

@@

I believe that the CS PhD programme at Stanford is perfect for me due to the following reasons. Firstly, the courses taught by world renown scientists e.g. Prof. Fei-Fei's ``High-Level Vision Behaviors, Neurons and Computational Models'' provide an extraordinary introduction to research in deep learning I would like to conduct. Secondly, research of the Stanford Visian Lab is multimodal in that it successfuly merges natural language processing with computer vision \cite{imageannot}. I find it very relevant, for it might lead to the improvement of living standard for people with impaired sight. Finally, Stanford is \emph{the} most exciting area for any computer scientist to live in. The diversity and the amount of talent there bolster personal development like no other place in the world.

>>>>

Artificial Intelligence has always tantalized me. Long before understanding what computer science stands for I wondered why AI has not been achieved yet. To explore it further, I enrolled in BSc in Robotics at the best technical university in my country. I studied maths, physics and mechanics, material science and manufacturing technologies; programming and software-oriented courses were my favourite, however. Paired with my passion for vision and perception, which I have developed as a photojournalist, it steered me towards my first computer vision course. I immediately knew that this intersection of image processing and machine learning was the area I wanted to focus on. It became apparent that pursuing a PhD was one of the few ways that could get me closer to solving the AI challenge.

@@

I believe that the CS PhD programme at the University of Toronto is perfect for me due to the following reasons. Firstly, the faculty has an extensive research experience in neural networks for computer vision, natural language and multi-modal settings.

Firstly, the courses taught by world renown scientists e.g. Prof. Raquel Urtasun and Prof. Richard Zemel ``Probabilistic Learning and Reasoning'' provide an extraordinary introduction to research in deep learning I would like to conduct. Secondly, research of the Machine Learning group at the U of T is multimodal in that it successfuly merges natural language processing with computer vision \cite{show}. I find it very relevant, for it might lead to the improvement of living standard for people with impaired sight.
